### 2018-09-24 ApproxComp/TKDE/sec-data.tex

@@

\begin{figure}[tb!]
  %\vspace{-1ex}
  \begin{center}
  \includegraphics[scale=0.45]{./dataApprox.png}
  \end{center}
  %\vspace{-1ex}
  \caption{Data approximation}\label{fig-tech-dataappro}
  \vspace{-2ex}
\end{figure}

\stitle{(2) Network Anomaly Detection~\cite{HuAMH16}}
Anomaly (or outlier) detection aims at identifying those objects in a database that are unusual, i.e., different than the majority of the data and therefore suspicious resulting from a contamination, error, or fraud~\cite{Zimek2017}. Network anomaly detection has become very popular
recently because of the importance of discovering key
regions of structural inconsistency in the network. In addition
to application-specific information carried by anomalies, the
presence of such structural inconsistency is often an impediment
to the effective application of data mining algorithms such as
community detection and classification.

@@

Dimensionality of embedding, each node is represented as a d-dimensional vector, can be large. Hence, such an approach is rather hard to apply to the case of large networks, because the complexity of the approach is in proportion to the square of the number of nodes when optimizing the embedding and because the noises in the embedding seriously impair the accuracy of detected anomalous nodes. Hence, we incorporate data approximation techniques (sampling, graph partitioning techniques, and, moreover, a novel dimension reduction technique) to make the approach more scalable and effective for large networks.

>>>>

\begin{figure}[tb!]
  %\vspace{-1ex}
  \begin{center}
  \includegraphics[scale=0.45]{./dataApprox.png}
  \end{center}
  %\vspace{-1ex}
  \caption{Data approximation}\label{fig-tech-dataappro}
  \vspace{-1ex}
\end{figure}

@@

\stitle{(2) Network Anomaly Detection~\cite{HuAMH16}}
Anomaly (or outlier) detection aims at identifying those objects in a dataset that are unusual, i.e., different than the majority and therefore suspicious resulting from a contamination, error, or fraud~\cite{Zimek2017}. Network anomaly detection has become very popular
recently because of the importance of discovering key
regions of structural inconsistency in the network. In addition
to application-specific information carried by anomalies, the
presence of such structural inconsistency is often an impediment
to the effective application of data mining algorithms such as
community detection and classification.

@@

For graph embedding, each node is represented as a d-dimensional vector, and the dimensionality $d$ can be large. Hence, such an approach is rather hard to apply to the case of large networks, because the complexity of the approach is in proportion to the square of the number of nodes when optimizing the embedding and because the noises in the embedding seriously impair the accuracy of detected anomalous nodes. Hence, we incorporate data approximation techniques (sampling, graph partitioning techniques, and, moreover, a novel dimension reduction technique) to make the approach more scalable and effective for large networks.
